Lawrence Bull, PhD

### 2024-04-02 index.qmd
glasgow

I'm interested in the dependencies that appear in measurements from populations of machines -- [planes](https://www.sciencedirect.com/science/article/pii/S0022460X21001449), [trains](https://arxiv.org/abs/2403.17820), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (... [wind turbines](https://arxiv.org/abs/2111.15496)).
By encoding domain expertise into statistical models, complex representations can be built from interpretable units, allowing machines to share information and increase the value of data.
<!-- At a systems level, alternative insights can emerge that might otherwise be missed -- the whole is something _besides_ its parts. -->

>>>>

I'm interested in the dependencies that appear in measurements from populations of machines -- [planes](https://www.sciencedirect.com/science/article/pii/S0022460X21001449), [trains](https://arxiv.org/abs/2403.17820), [automobiles](https://doi.org/10.48550/arXiv.2204.12404) (... [wind turbines](https://arxiv.org/abs/2111.15496)).
By encoding domain expertise into statistical models, complex representations can be built from interpretable units, allowing machines to share information and increasing the value of data.
<!-- At a systems level, alternative insights can emerge that might otherwise be missed -- the whole is something _besides_ its parts. -->
